Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-02-28 05_AUDPC_MetaAnalysis.Rmd
Change data/ location to cache/

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor)

# Data
PM_Mdat <- read.csv("data/GYmeta_data.csv")
```

>>>>

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor, here)

# Data
PM_Mdat <- read.csv(here("cache/GYmeta_data.csv"))
```
